\bf The EPEC Model

### 2021-07-11 Documentation/EPEC_Model.tex
Updated FLUX documentation
Added bootstrap terms

\documentclass[12pt,prb,aps]{revtex4-2}
\usepackage {amsmath}
\pdfoutput = 1 
\usepackage {graphicx}
\allowdisplaybreaks

\begin{document}
\title{\bf The EPEC Model}
\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}}
\affiliation{Institute for Fusion Studies,  Department of Physics,  University of Texas at Austin,  Austin TX 78712, USA}

\maketitle

@@

The EPEC model determines the elements of the $E_{kk'}$ matrix using a high-$q$ approximation. In fact, if $F_{kk'}$ is the inverse of the $E_{kk'}$ matrix then
\begin{equation}\label{e56}
F_{kk'} = \oint\oint 
G(R_k,Z_k;R_{k'},Z_{k'})\,{\rm e}^{-{\rm i}\,(m_k\,\theta_k-m_{k'}\,\theta_{k'})}\,\frac{d\theta_k}{2\pi}\,\frac{d\theta_{k'}}{2\pi},
\end{equation}
and
\begin{align}
 G(R_k,Z_k;R_{k'},Z_{k'})&= \frac{(-1)^{\,n}\,\pi^{\,2}\,R_k\,R_{k'}/R_0}{2\,\Gamma(1/2)\,\Gamma(n+1/2)}
\left[\frac{\cosh\eta_{kk'}}{R_k^{\,2}+R_{k'}^{\,2}+(Z_k-Z_{k'})^{\,2}}\right]^{1/2}\nonumber\\[0.5ex]
&\times\left[(n-1/2)\,P_{-1/2}^{\,n-1}(\cosh\eta_{kk'})+
\frac{P_{-1/2}^{\,n+1}(\cosh\eta_{kk'})}{n+1/2}\right],
\end{align}
with
\begin{equation}
\eta_{kk'} = \tanh^{-1}\left[\frac{2\,R_k\,R_{k'}}{R_k^{\,2}+R_{k'}^{\,2}+(Z_k-Z_{k'})^{\,2}}\right].
\end{equation}
Here, the double integral in Eq.~(\ref{e56}) is taken around the
$k$th resonant surface (cylindrical coordinates $R_k$, $0$, $Z_k$;
flux coordinates $r_k$, $\theta_k$, $0$, with $r_k$ constant; resonant poloidal mode number $m_k$) and the $k'$th resonant surface (cylindrical coordinates $R_{k'}$, $0$, $Z_{k'}$;
flux coordinates $r_{k'}$, $\theta_{k'}$, $0$, with $r_{k'}$ constant; resonant poloidal mode number $m_{k'}$). Finally, the $\Gamma(z)$ and $P_\mu^{\,\nu}(z)$ are Gamma functions and associated Legendre functions, respectively.

@@

\section{Neoclassical Physics}\label{appb}
\subsection{Plasma Species}\label{a3}
The plasma is assumed to consist of three (charged) species; namely,  electrons ($e$), majority ions ($i$), and impurity ions
($I$).  The charges of the  three species are $e_e=-e$, $e_i= e$, and $e_I=Z_I\,e$, respectively, where
$e$ is the magnitude of the electron charge. 
Quasi-neutrality demands that
$n_e= n_i+ Z_I\,n_I$, where $n_a(r)$ is the species-$a$ number density. 
 Let 
$\alpha_I(r) =Z_I\,(Z_{\rm eff}-1)/(Z_I-Z_{\rm eff})$,
where 
$Z_{\rm eff}(r) = (n_i+Z_I^{\,2}\,n_I)/n_e$
is the effective ion charge number. It follows that
$n_i/n_e = (Z_I-Z_{\rm eff})/(Z_I-1)$
and
$n_I/n_e= (Z_{\rm eff}-1)/[Z_I\,(Z_I-1)]$.

@@

The $2\times 2$ dimensionless electron collisional friction matrix, $[F^{\,ee}](r)$,   is defined to have the following elements:
$F^{\,ee}_{00} = Z_{\rm eff}$,
$F^{\,ee}_{01} = (3/2)\,Z_{\rm eff}$,
$F^{\,ee}_{10} = F^{\,ee}_{01}$,
$F^{\,ee}_{11}= \sqrt{2} + (13/4)\,Z_{\rm eff}$.

@@

\subsection{Parallel Force and Heat Balance}\label{sbalance}
Let
$[\tilde{\mu}^{\,I}] =\alpha_I^{\,2}\,(T_i/T_I)\,x_{Ii}\,[\mu^{\,I}]$.
The requirement of equilibrium force and heat balance parallel to the magnetic field leads us to define
four $2\times 2$  dimensionless ion matrices, $[L^{\,ii}](r)$, $[L^{\,iI}](r)$, $[L^{\,Ii}](r)$, and $[L^{\,II}](r)$,
where
\begin{align}
\left(\begin{array}{cc} [L^{\,ii}], & [L^{\,iI}]\\[0.5ex] [L^{\,Ii}],& [L^{\,II}]\end{array}\right)=
\left(\begin{array}{cc}[F^{\,ii}+\mu^{\,i}+ Y^{\,in}/y_n], & -[F^{\,iI}]\\[0.5ex] -[F^{\,Ii}], & [F^{\,II}+\tilde{\mu}^{\,I}]\end{array}\right)^{-1}
\left(\begin{array}{cc} [F^{\,ii}+Y^{\,in}], & -[F^{\,iI}]\\[0.5ex] -[F^{\,Ii}], & [F^{\,II}]\end{array}\right),
\end{align}
the additional  four $2\times 2$  dimensionless ion matrices, $[G^{\,ii}](r)$, $[G^{\,iI}](r)$, $[G^{\,Ii}](r)$, and $[G^{\,II}](r)$,
where
\begin{align}
\left(\begin{array}{cc} [G^{\,ii}], & [G^{\,iI}]\\[0.5ex] [G^{\,Ii}],& [G^{\,II}]\end{array}\right)=\tau_{ii}\,\langle \sigma\,v\rangle_i^{\,\rm cx}
\,\langle n_n\rangle
\left(\begin{array}{cc}[F^{\,ii}+\mu^{\,i}+ Y^{\,in}/y_n], & -[F^{\,iI}]\\[0.5ex] -[F^{\,Ii}], & [F^{\,II}+\tilde{\mu}^{\,I}]\end{array}\right)^{-1},
\end{align}
and the $2\times 2$ dimensionless electron matrix, $[Q^{\,ee}](r)$, 
where
$[Q^{\,ee}]= [F^{\,ee}+\mu^{\,e}]^{\,-1}$.
Here,
\begin{align}
[Y^{\,in}] &= \tau_{ii}\,\langle \sigma\,v\rangle_i^{\,\rm cx}
\,\langle n_n\rangle\left[
\begin{array}{cc} 1,& 0\\[0.5ex]0,&E_n/T_i\end{array}
\right],\\[0.5ex]
y_n &= \frac{\langle n_n\rangle\,\langle B^{\,2}\rangle}{\langle
n_n\,B^{\,2}\rangle},
\end{align}
where
\begin{equation}
\langle A\rangle (r) \equiv\left.\oint \frac{A(r,{\mit\Theta})\,d{\mit\Theta}}{B(r,{\mit\Theta})}\right/\oint \frac{d{\mit\Theta}}{B(r,{\mit\Theta})}.
\end{equation}
Moreover, $\langle \sigma\,v\rangle_i^{\,\rm cx}$ is the flux-surface
averaged rate constant for charge exchange reactions between neutrals and majority ions, $n_n(r,{\mit\Theta})$  the
neutral particle number density, and $E_n/T_i$ the ratio of the incoming neutral energy to the majority ion energy. The parameter
$y_n$ takes into account the fact that the incoming neutrals at the
edge of an H-mode tokamak plasma are usually
concentrated at the X-point (i.e., $y_n>1$).

\subsection{Impurity Ion Angular Rotation Velocities}\label{srotation}
Let
\begin{align}
\omega_{\theta\,I}(r)&=\frac{{\bf V}^{\,I}\cdot\nabla\theta}{{\bf B}\cdot\nabla\theta}\,\frac{R_0\,B_0\,g}{R^{\,2}},\\[0.5ex]
\omega_{\phi\,I}(r) &= {\bf V}^{\,I}\cdot\nabla\phi,
\end{align}
where ${\bf V}^{\,I}$ is the impurity ion fluid velocity, and the right-hand sides are evaluated on the outboard mid-plane. According to neoclassical theory
\begin{align}
\omega_{\theta\,I} &= K_\theta\,\omega_{{\rm nc}\,I},\\[0.5ex]
\omega_{\phi\,I} &= \omega_E+\omega_{\ast\,I} + \omega_{\theta\,I},
\end{align}
where
\begin{equation}
K_\theta(r) = \frac{R_0^{\,2}\,B_0^{\,2}\,g^{\,2}}{R^{\,2}\,\langle B^{\,2}\rangle},
\end{equation}
\begin{align}
\omega_E(r) &=-\frac{d{\mit\Phi}}{d{\mit\Psi}_p},\\[0.5ex]
\omega_{\ast\,a}(r) &= -\frac{T_a}{e_a}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
\eta_a(r) &= \frac{d\ln T_a}{d\ln n_a}.
\end{align}
and 
\begin{align}\label{a53}
\omega_{{\rm nc}\,I}(r)&=-G_{00}^{\,Ii}\,\omega_E -\left[L^{\,II}_{00}-L^{\,II}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}-
\left[L^{\,Ii}_{00}-L^{\,Ii}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i}.
\end{align}
Here, $p_a(r)=n_a\,T_a$, and ${\mit\Phi}(r)$ is the equilibrium electric scalar potential.

\section{Plasma Response in Inner Region}
\subsection{Evolution Equations}
Let ${\mit\Psi}_k= R_0\,B_0\,\hat{\mit\Psi}_k\,{\rm e}^{-{\rm i}\,\varphi_k}$, ${\mit\chi}_k= R_0\,B_0\,\hat{\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$, and $E_{kk'}=\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$,
where $\hat{\mit\Psi}_k>0$, $\varphi_k$, $\hat{\chi}_k>0$, $\zeta_k$, $\hat{E}_{kk}'>0$, and $\xi_{kk'}$ are all real quantities. Furthermore,
let $X_k= \hat{\mit\Psi}_k\,\cos\varphi_k$ and $Y_k= \hat{\mit\Psi}_k\,\sin\varphi_k$. The resonant plasma response model at the 
$k$th resonant surface takes the form
\begin{align}\label{e21}
\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
+\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k,\\[0.5ex]
\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k,\label{e22}
\end{align}
where
\begin{align}\label{e23}
{\cal S}_k&=\frac{\tau_R(r_k)}{\tau_A},\\[0.5ex]
\tau_A &= \left[\frac{\mu_0\,\rho(0)\,r_{100}^{\,2}}{B_0^{\,2}}\right]^{1/2},\\[0.5ex]
\tau_R(r) &= \mu_0\,r^{\,2}\,\sigma_{ee}\,Q_{00}^{ee},\\[0.5ex]
\sigma_{ee}(r) &=\frac{n_e\,e^{\,2}\,\tau_{ee}}{m_e},\\[0.5ex]
\hat{W}_k &=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
s(r) &= \frac{d\ln q}{d\ln r},\\[0.5ex]
\hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k}.
\end{align}
Here, ${\cal I}=0.8227$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, and $\hat{t}=t/\tau_A$. Furthermore, $\delta_{\rm linear}(r)$ is the linear layer width, whereas $\rho(r)$ is the plasma
mass density profile.

>>>>

\documentclass[notitlepage,12pt,prb,aps]{revtex4-1}
\usepackage {amsmath}
\pdfoutput = 1 
\usepackage {graphicx}
\allowdisplaybreaks

\begin{document}
\title{\bf The EPEC Model}
\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}}
\affiliation{Institute for Fusion Studies,  Department of Physics,  University of Texas at Austin,  Austin TX 78712, USA}
\date{\today}
\maketitle

@@

The EPEC model determines the elements of the $E_{kk'}$ matrix using a high-$q$ approximation. In fact, if $F_{kk'}$ is the inverse of the $E_{kk'}$ matrix then
\begin{equation}\label{e56}
F_{kk'} = \oint\oint 
G(R_k,Z_k;R_{k'},Z_{k'})\,{\rm e}^{-{\rm i}\,(m_k\,\theta_k-m_{k'}\,\theta_{k'})}\,\frac{d\theta_k}{2\pi}\,\frac{d\theta_{k'}}{2\pi},
\end{equation}
and
\begin{align}
 G(R_k,Z_k;R_{k'},Z_{k'})&= \frac{(-1)^{\,n}\,\pi^{\,2}\,R_k\,R_{k'}/R_0}{2\,{\mit\Gamma}(1/2)\,{\mit\Gamma}(n+1/2)}
\left[\frac{\cosh\eta_{kk'}}{R_k^{\,2}+R_{k'}^{\,2}+(Z_k-Z_{k'})^{\,2}}\right]^{1/2}\nonumber\\[0.5ex]
&\times\left[(n-1/2)\,P_{-1/2}^{\,n-1}(\cosh\eta_{kk'})+
\frac{P_{-1/2}^{\,n+1}(\cosh\eta_{kk'})}{n+1/2}\right],
\end{align}
with
\begin{equation}
\eta_{kk'} = \tanh^{-1}\left[\frac{2\,R_k\,R_{k'}}{R_k^{\,2}+R_{k'}^{\,2}+(Z_k-Z_{k'})^{\,2}}\right].
\end{equation}
Here, the double integral in Eq.~(\ref{e56}) is taken around the
$k$th resonant surface (cylindrical coordinates $R_k$, $0$, $Z_k$;
flux coordinates $r_k$, $\theta_k$, $0$, with $r_k$ constant; resonant poloidal mode number $m_k$) and the $k'$th resonant surface (cylindrical coordinates $R_{k'}$, $0$, $Z_{k'}$;
flux coordinates $r_{k'}$, $\theta_{k'}$, $0$, with $r_{k'}$ constant; resonant poloidal mode number $m_{k'}$). Finally, the ${\mit\Gamma}(z)$ and $P_\mu^{\,\nu}(z)$ are gamma functions and associated Legendre functions, respectively.

@@

\section{Neoclassical Physics}\label{appb}
\subsection{Plasma Species}\label{a3}
The plasma is assumed to consist of three (charged) species; namely,  electrons ($e$), majority ions ($i$), and impurity ions
($I$).  The charges of the  three species are $e_e=-e$, $e_i= e$, and $e_I=Z_I\,e$, respectively, where
$e$ is the magnitude of the electron charge. 
Quasi-neutrality demands that
$n_e= n_i+ Z_I\,n_I$, where $n_a(r)$ is the species-$a$ number density. 
 Let 
$\alpha_I(r) =Z_I\,(Z_{\rm eff}-1)/(Z_I-Z_{\rm eff})$,
where 
$Z_{\rm eff}(r) = (n_i+Z_I^{\,2}\,n_I)/n_e$
is the effective ion charge number. It follows that
$n_i/n_e = (Z_I-Z_{\rm eff})/(Z_I-1)$
and
$n_I/n_e= (Z_{\rm eff}-1)/[Z_I\,(Z_I-1)]$. Finally, let $Z_{{\rm eff}\,i}= (Z_I-Z_{\rm eff})/(Z_I-1)$, and
$Z_{{\rm eff}\,I}=Z_I\,(Z_{\rm eff}-1)/(Z_I-1)$. Note that $Z_{\rm eff}= Z_{{\rm eff}\,i}+ Z_{{\rm eff}\,I}$.

@@

The $2\times 2$ dimensionless electron collisional friction matrices, $[F^{\,ee}](r)$,   $[F^{\,ei}](r)$, and
$[F^{\,eI}](r)$, are defined to have the following elements:
$F^{\,ee}_{00} = Z_{\rm eff}$,
$F^{\,ee}_{01} = (3/2)\,Z_{\rm eff}$,
$F^{\,ee}_{10} = F^{\,ee}_{01}$,
$F^{\,ee}_{11}= \sqrt{2} + (13/4)\,Z_{\rm eff}$, $F^{\,ei}_{00} = Z_{{\rm eff}\,i}$,
$F^{\,ei}_{01} =F^{\,ei}_{11}=0$, $F^{\,ei}_{10}=(3/2)\,Z_{{\rm eff}\,i}$,  $F^{\,eI}_{00} = Z_{{\rm eff}\,I}$,
$F^{\,eI}_{01} =F^{\,eI}_{11}=0$, $F^{\,eI}_{10}=(3/2)\,Z_{{\rm eff}\,I}$.

@@

\subsection{Parallel Force and Heat Balance}\label{sbalance}
Let
$[\tilde{\mu}^{\,I}] =\alpha_I^{\,2}\,(T_i/T_I)\,x_{Ii}\,[\mu^{\,I}]$.
The requirement of equilibrium force and heat balance parallel to the magnetic field leads us to define
four $2\times 2$  dimensionless ion matrices, $[L^{\,ii}](r)$, $[L^{\,iI}](r)$, $[L^{\,Ii}](r)$, and $[L^{\,II}](r)$,
where
\begin{align}
\left(\begin{array}{cc} [L^{\,ii}], & [L^{\,iI}]\\[0.5ex] [L^{\,Ii}],& [L^{\,II}]\end{array}\right)=
\left(\begin{array}{cc}[F^{\,ii}+\mu^{\,i}+ Y^{\,in}/y_n], & -[F^{\,iI}]\\[0.5ex] -[F^{\,Ii}], & [F^{\,II}+\tilde{\mu}^{\,I}]\end{array}\right)^{-1}
\left(\begin{array}{cc} [F^{\,ii}+Y^{\,in}], & -[F^{\,iI}]\\[0.5ex] -[F^{\,Ii}], & [F^{\,II}]\end{array}\right),
\end{align}
the additional  four $2\times 2$  dimensionless ion matrices, $[G^{\,ii}](r)$, $[G^{\,iI}](r)$, $[G^{\,Ii}](r)$, and $[G^{\,II}](r)$,
where
\begin{align}
\left(\begin{array}{cc} [G^{\,ii}], & [G^{\,iI}]\\[0.5ex] [G^{\,Ii}],& [G^{\,II}]\end{array}\right)=\tau_{ii}\,\langle \sigma\,v\rangle_i^{\,\rm cx}
\,\langle n_n\rangle
\left(\begin{array}{cc}[F^{\,ii}+\mu^{\,i}+ Y^{\,in}/y_n], & -[F^{\,iI}]\\[0.5ex] -[F^{\,Ii}], & [F^{\,II}+\tilde{\mu}^{\,I}]\end{array}\right)^{-1},
\end{align}
and the $2\times 2$ dimensionless electron matrices, $[Q^{\,ee}](r)$, $[G^{\,ei}](r)$, $[L^{\,ee}](r)$, $[L^{\,ei}](r)$, 
and $[L^{\,eI}](r)$, 
where
\begin{align}
[Q^{\,ee}]&= [F^{\,ee}+\mu^{\,e}]^{\,-1},\\[0.5ex]
[G^{\,ei}] &= [Q^{\,ee}]\,([F^{\,ei}]\,[G^{\,ii}]+ [F^{\,eI}]\,[G^{\,Ii}]),\\[0.5ex]
[L^{\,ee}] &= [Q^{\,ee}]\,[F^{\,ee}],\\[0.5ex]
[L^{\,ei}] &= [Q^{\,ee}]\left\{[F^{\,ei}\,]\,[L^{\,ii}]-[F^{\,ei}]+[F^{\,eI}]\,[L^{\,Ii}]\right\},\\[0.5ex]
[L^{\,eI}] &= [Q^{\,ee}]\left\{[F^{\,eI}]\,[L^{\,II}]-[F^{\,eI}]+[F^{\,ei}]\,[L^{\,iI}]\right\}.
\end{align}
Here,
\begin{align}
[Y^{\,in}] &= \tau_{ii}\,\langle \sigma\,v\rangle_i^{\,\rm cx}
\,\langle n_n\rangle\left[
\begin{array}{cc} 1,& 0\\[0.5ex]0,&E_n/T_i\end{array}
\right],\\[0.5ex]
y_n &= \frac{\langle n_n\rangle\,\langle B^{\,2}\rangle}{\langle
n_n\,B^{\,2}\rangle},
\end{align}
where
\begin{equation}
\langle A\rangle (r) \equiv\left.\oint \frac{A(r,{\mit\Theta})\,d{\mit\Theta}}{B(r,{\mit\Theta})}\right/\oint \frac{d{\mit\Theta}}{B(r,{\mit\Theta})}.
\end{equation}
Moreover, $\langle \sigma\,v\rangle_i^{\,\rm cx}$ is the flux-surface
averaged rate constant for charge exchange reactions between neutrals and majority ions, $n_n(r,{\mit\Theta})$  the
neutral particle number density, and $E_n/T_i$ the ratio of the incoming neutral energy to the majority ion energy. The parameter
$y_n$ takes into account the fact that the incoming neutrals at the
edge of an H-mode tokamak plasma are usually
concentrated at the X-point (i.e., $y_n>1$).

\subsection{Neoclassical Frequencies}
The neoclassical frequencies of the three plasma species have the following definitions:
\begin{align}
\omega_{{\rm nc}\,i}(r)&=-G_{00}^{\,ii}\,\omega_E -\left[L^{\,ii}_{00}-L^{\,ii}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i}-
\left[L^{\,iI}_{00}-L^{\,iI}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I},\\[0.5ex]
\omega_{{\rm nc}\,I}(r)&=-G_{00}^{\,Ii}\,\omega_E -\left[L^{\,II}_{00}-L^{\,II}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}-
\left[L^{\,Ii}_{00}-L^{\,Ii}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i},\\[0.5ex]
\omega_{{\rm nc}\,e}(r)&=-G_{00}^{\,ei}\,\omega_E -\left[L^{\,ee}_{00}-L^{\,ee}_{01}\left(\frac{\eta_e}{1+\eta_e}\right)\right]\omega_{\ast\,e}-
\left[L^{\,ei}_{00}-L^{\,ei}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i}\nonumber\\[0.5ex]
&\phantom{=}-
\left[L^{\,eI}_{00}-L^{\,eI}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}.
\end{align}
Here,
\begin{align}
\omega_E(r) &=-\frac{d{\mit\Phi}}{d{\mit\Psi}_p},\\[0.5ex]
\omega_{\ast\,a}(r) &= -\frac{T_a}{e_a}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
\eta_a(r) &= \frac{d\ln T_a}{d\ln n_a}.
\end{align}
Moreover, $p_a(r)=n_a\,T_a$, and ${\mit\Phi}(r)$ is the equilibrium electric scalar potential.

\subsection{Impurity Ion Angular Rotation Velocities}\label{srotation}
Let
\begin{align}
\omega_{\theta\,I}(r)&=\frac{{\bf V}^{\,I}\cdot\nabla\theta}{{\bf B}\cdot\nabla\theta}\,\frac{R_0\,B_0\,g}{R^{\,2}},\\[0.5ex]
\omega_{\phi\,I}(r) &= {\bf V}^{\,I}\cdot\nabla\phi,
\end{align}
where ${\bf V}^{\,I}$ is the impurity ion fluid velocity, and the right-hand sides are evaluated on the outboard mid-plane. According to neoclassical theory,
\begin{align}
\omega_{\theta\,I} &= K_\theta\,\omega_{{\rm nc}\,I},\\[0.5ex]
\omega_{\phi\,I} &= \omega_E+\omega_{\ast\,I} + \omega_{\theta\,I},
\end{align}
where
\begin{equation}
K_\theta(r) = \frac{R_0^{\,2}\,B_0^{\,2}\,g^{\,2}}{R^{\,2}\,\langle B^{\,2}\rangle}.
\end{equation}

\section{Plasma Response in Inner Region}
\subsection{Evolution Equations}
Let ${\mit\Psi}_k= R_0\,B_0\,\hat{\mit\Psi}_k\,{\rm e}^{-{\rm i}\,\varphi_k}$, ${\mit\chi}_k= R_0\,B_0\,\hat{\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$, and $E_{kk'}=\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$,
where $\hat{\mit\Psi}_k>0$, $\varphi_k$, $\hat{\chi}_k>0$, $\zeta_k$, $\hat{E}_{kk}'>0$, and $\xi_{kk'}$ are all real quantities. Furthermore,
let $X_k= \hat{\mit\Psi}_k\,\cos\varphi_k$ and $Y_k= \hat{\mit\Psi}_k\,\sin\varphi_k$. The resonant plasma response model at the 
$k$th resonant surface takes the form
\begin{align}\label{e21}
&\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
+\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k\nonumber\\[0.5ex]&\phantom{=====} +\frac{\alpha_{b\,e\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{e}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_e}^{\,2}+W_k^{\,2}}\right)X_k+\frac{\alpha_{b\,i\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_i}^{\,2}+\hat{W}_k^{\,2}}\right)X_k\nonumber\\[0.5ex]
&\phantom{=====}+\frac{\alpha_{c\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}\right)X_k+\frac{\alpha_{p\,k}}{\hat{W}_k^{\,3}}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{W}_k^{\,2}}\right)^2 X_k,\\[0.5ex]
&\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k\nonumber\\[0.5ex]&\phantom{=====} +\frac{\alpha_{b\,e\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{e}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_e}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k+\frac{\alpha_{b\,i\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_i}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k\nonumber\\[0.5ex]
&\phantom{=====}+\frac{\alpha_{c\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k+\frac{\alpha_{p\,k}}{\hat{W}_k^{\,3}}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{W}_k^{\,2}}\right)^2 Y_k,\label{e22}
\end{align}
where
\begin{align}\label{e23}
{\cal S}_k&=\frac{\tau_R(r_k)}{\tau_A},\\[0.5ex]
\tau_A &= \left[\frac{\mu_0\,\rho(0)\,r_{100}^{\,2}}{B_0^{\,2}}\right]^{1/2},\\[0.5ex]
\tau_R(r) &= \mu_0\,r^{\,2}\,\sigma_{ee}\,Q_{00}^{ee},\\[0.5ex]
\sigma_{ee}(r) &=\frac{n_e\,e^{\,2}\,\tau_{ee}}{m_e},\\[0.5ex]
\hat{W}_k &=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
\hat{W}_{T_e\,k} &= 2\,{\cal I}\left(\frac{\chi_e\,R_0}{v_{T\,e}\,r^{\,2}\,s\,n}\right)^{1/3}_{r_k},\\[0.5ex]
\hat{W}_{T_i\,k} &= 2\,{\cal I}\left(\frac{\chi_i\,R_0}{v_{T\,e}\,r^{\,2}\,s\,n}\right)^{1/3}_{r_k},\\[0.5ex]
\hat{W}_{n_e\,k} &= 2\,{\cal I}\left(\frac{D_\perp\,R_0}{v_{T\,e}\,r^{\,2}\,s\,n}\right)^{1/3}_{r_k},\\[0.5ex]
s(r) &= \frac{d\ln q}{d\ln r},\\[0.5ex]
\hat{\rho}_{\theta\,e} &= \left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
\hat{\rho}_{\theta\,i} &= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
\hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k},\\[0.5ex]
\alpha_{b\,e\,k} &= -2\,{\cal I}\,I_g\left(\frac{\omega_{\ast\,e}+\omega_{{\rm nc}\,e}}{\omega_\beta}\right)_{r_k},\\[0.5ex]
\alpha_{b\,i\,k} &= 2\,{\cal I}\,I_g\left[\frac{(n_i/n_e)\left(\omega_{\ast\,i}+\omega_{{\rm nc}\,i}\right)+(Z_I\,n_I/n_e)\left(\omega_{\ast\,I}+\omega_{{\rm nc}\,I}\right)}{\omega_\beta}\right]_{r_k},\\[0.5ex]
\alpha_{c\,k} &= 2\,{\cal I}\,I_g\,D_R(r_k),\\[0.5ex]
\alpha_{p\,k} &= 8\,{\cal I}^{\,3}\, I_p\left[\frac{(\omega_{\ast\,i}+\omega_{{\rm nc}\,i})\,\omega_{{\rm nc}\,i}}{\omega_\beta\,\omega_{\mit\Omega}}\right]_{r_k},\\[0.5ex]
\omega_{\beta}(r)&= \frac{s\,g\,B_0}{\mu_0\,n_e\,e\,R_0^{\,2}\,q},\\[0.5ex]
\omega_{\mit\Omega}(r)&= \frac{e\,g\,B_0\,s\,q}{m_i}.
\end{align}
Here, ${\cal I}=0.8227$, $I_g=1.58$, $I_p=1.38$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, and $\hat{t}=t/\tau_A$. Furthermore, $\delta_{\rm linear}(r)$ is the linear layer width, whereas $\rho(r)$ is the plasma
mass density profile. Moreover, $\chi_e(r)$, $\chi_i(r)$, and $D_\perp(r)$ are the perpendicular electron
energy, ion energy, and particle diffusivity profile, respectively.
